Single Higgs backgrounds for $HH\to4b$

### 2016-03-02 doc/singleHbkgs/singleHbkgs.tex
single H background docs

\title{Multiplicative factors for H backgrounds}
\begin{document}
\maketitle

@@

\begin{table}[htp]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Sample & Decay & BF & Ref\\
\hline\hline
$ZH$ & ($Z\to b\bar{b}$)($H\to b\bar{b}$) & 0.0861 & \cite{Agashe:2014kda}\\
$ttH$ & $(W\to q\bar{q})^2$($H\to b\bar{b}$) & 0.259 & \cite{Agashe:2014kda}\\
\hline
\end{tabular}
\end{center}
\label{HBF}
\caption{Branching fractions for single Higgs backgrounds.}
\end{table}%
\begin{thebibliography}{9}

>>>>

\title{Single Higgs backgrounds for $HH\to4b$}
\begin{document}
\maketitle

@@

\begin{table}[htp]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Sample & Decay & BF & Ref\\
\hline\hline
$ZH$ & ($Z\to b\bar{b}$)($H\to b\bar{b}$) & 0.0861 & \cite{Agashe:2014kda}\\
$ttH$ & $(W\to q\bar{q})^2$($H\to b\bar{b}$) & 0.259 & \cite{Agashe:2014kda}\\
$bbH$ & $H\to b\bar{b}$ & 0.57 & \cite{Agashe:2014kda} \\
\hline
\end{tabular}
\end{center}
\label{HBF}
\caption{Branching fractions for single Higgs backgrounds.}
\end{table}%

\begin{table}[htp]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
Sample & Boosted (fb) & Intermediate (fb) & Resolved (fb) \\
\hline\hline
$ZH$ & $2.014\cdot 10^{-2}$ & $1.208\cdot 10^{-1}$ & $7.490\cdot 10^{-1}$ \\
$ttH$ & $5.058\cdot 10^{-2}$ & $6.325\cdot 10^{-3}$ & $4.054\cdot 10^{-1}$ \\
$bbH$ & $2.282\cdot 10^{-3}$ & $5.548\cdot 10^{-3}$ & $2.609\cdot 10^{-1}$\\
\hline\hline
$HH$ & $3.556\cdot 10^{-1}$  & $2.238\cdot 10^{-1}$ &  $1.237\cdot 10^{0}$ \\
QCD &  $2.533\cdot 10^{2}$ & $1.771\cdot 10^{2}$ & $4.866\cdot 10^{3}$ \\
\hline
\end{tabular}
\end{center}
\label{HBF}
\caption{ Results of running the OHH4b analysis code over the single Higgs background samples (noPU, pre-MVA). The numbers here are the cross sections remaining in the various channels and topologies after all analysis cuts. Also given for comparison are the post-analysis cross sections for the diHiggs signal and QCD background.}
\end{table}%

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/res.pdf}
\includegraphics[width=0.45\textwidth]{plots/inter.pdf}
\includegraphics[width=\textwidth]{plots/boost.pdf}
\caption{Cutflows for the resolved (top-left), intermediate (top-right) and boosted (bottom) analyses of single Higgs backgrounds.}
\end{center}
\end{figure}

\begin{thebibliography}{9}
